My english activity log

### 2019-10-27 english-activity.Rmd
(jusqu'au 20/10/2019)
jusqu'au 27/10/2019

19/10/2019 : I watched a video about marine biology https://www.youtube.com/watch?v=uWZXC3mjeZU.

@@

>>>>

19/10/2019 : I watched a video about marine biology https://www.youtube.com/watch?v=uWZXC3mjeZU. I also read the fouth chapter of "The Hobbit".

@@

22/10/2019 : I watched a video about predation https://www.youtube.com/watch?v=6jXwEOit5vM.

24/10/2019 : I watched a video about genetic drift https://www.youtube.com/watch?v=W0TM4LQmoZY and a video about natural selection https://www.youtube.com/watch?v=7VM9YxmULuo.

26/10/2019 : I watched a video about the loss of biodiversity https://www.youtube.com/watch?v=vCkDxD0DV0Q and I read the fifth chapter of "T he Hobbit".

27/10/2019 : I watched a video about the protein structure and folding https://www.youtube.com/watch?v=hok2hyED9go.
